EldersAIR initial home/adult data work

### 2021-03-01 elders_health_data_cleaning.Rmd
data cleaning updates

---
title: "Elders health and elder files data cleaning"
author: "Ethan Walker"
date: "Started 28 Feb 2020, Updated 28 Feb 2020"
output: pdf_document 
---

@@

# Load and merge files from different locations
```{r}
nn_athomelog_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_athome_20200225.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NN",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         at_home_7 = as.factor(AtHome1),
         at_home_8 = as.factor(AtHome2),
         at_home_9 = as.factor(AtHome3),
         at_home_10 = as.factor(AtHome4),
         at_home_11 = as.factor(AtHome5),
         at_home_12 = as.factor(AtHome6),
         at_home_13 = as.factor(AtHome7),
         at_home_14 = as.factor(AtHome8),
         at_home_15 = as.factor(AtHome9),
         at_home_16 = as.factor(AtHome10),
         at_home_17 = as.factor(AtHome11),
         at_home_18 = as.factor(AtHome12),
         at_home_19 = as.factor(AtHome13),
         at_home_20 = as.factor(AtHome14),
         at_home_21 = as.factor(AtHome15),
         at_home_22 = as.factor(AtHome16)) %>% 
  select(home_winter_id:at_home_22)

np_athomelog_initial <- read_xlsx(paste0(file_path, "Input/NP/np_athomelog_20200225.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NP",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         at_home_7 = as.factor(AtHome1),
         at_home_8 = as.factor(AtHome2),
         at_home_9 = as.factor(AtHome3),
         at_home_10 = as.factor(AtHome4),
         at_home_11 = as.factor(AtHome5),
         at_home_12 = as.factor(AtHome6),
         at_home_13 = as.factor(AtHome7),
         at_home_14 = as.factor(AtHome8),
         at_home_15 = as.factor(AtHome9),
         at_home_16 = as.factor(AtHome10),
         at_home_17 = as.factor(AtHome11),
         at_home_18 = as.factor(AtHome12),
         at_home_19 = as.factor(AtHome13),
         at_home_20 = as.factor(AtHome14),
         at_home_21 = as.factor(AtHome15),
         at_home_22 = as.factor(AtHome16)) %>% 
  select(home_winter_id:at_home_22)

# Combine logs from all areas
elders_at_home_log <- rbind(nn_athomelog_initial, np_athomelog_initial) %>% 
  left_join(elders_ids_linked, c("area", "home_winter_id", "adult_id_num"))
# write_rds(elders_at_home_log, "Output/elders_at_home_log.rds")

@@

write_csv(save_var_names, paste0(file_path, "Output/at_home_var_names.csv"))
```

@@

# Load and merge files from different locations
```{r}
nn_healthhistory_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_healthhistory_20200225.xlsx")) %>% 
  rename_all(~str_replace_all(., "Date", "_date")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NN",
         rheum_arth = ra,
         rheum_arth_date = ra_date) %>% 
  select(-id:-homewinterid, -ra, -ra_date, -whatmissing:-ignorereason) %>% 
  select(home_winter_id, adult_id_num, area, rheum_arth, rheum_arth_date,
         lupus:cigarspipes)

np_healthhistory_initial <- read_xlsx(paste0(file_path, "Input/NP/np_healthhistory_20200225.xlsx")) %>% 
  rename_all(~str_replace_all(., "Date", "_date")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NP",
         rheum_arth = ra,
         rheum_arth_date = ra_date) %>% 
  select(-id:-homewinterid, -ra, -ra_date, -whatmissing:-ignoremissingdata) %>% 
  select(home_winter_id, adult_id_num, area, rheum_arth, rheum_arth_date,
         lupus:cigarspipes)

# Combine logs from all areas
elders_health_hx <- rbind(nn_healthhistory_initial, np_healthhistory_initial) %>% 
  left_join(elders_ids_linked, c("area", "home_winter_id", "adult_id_num"))
# write_rds(elders_health_hx, "Output/elders_health_hx.rds")

@@

write_csv(save_var_names, paste0(file_path, "Output/health_hx_var_names.csv"))
```

@@

# Load and merge files from different locations
```{r}
nn_healthextra_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_healthextra_20200225.xlsx")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NN",
         sampling_visit = samplingvisit) %>% 
  select( home_winter_id, adult_id_num, sampling_visit, area, cold2m:bronch2mdr)

np_healthextra_initial <- read_xlsx(paste0(file_path, "Input/NP/np_healthextra_20200225.xlsx")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NP",
         sampling_visit = samplingvisit) %>% 
  select( home_winter_id, adult_id_num, sampling_visit, area, cold2m:bronch2mdr)

# Combine logs from all areas
elders_health_extra <- rbind(nn_healthextra_initial, np_healthextra_initial) %>% 
  left_join(elders_ids_linked, c("area", "home_winter_id", "adult_id_num"))
# write_rds(elders_health_extra, "Output/elders_health_extra.rds")

@@

write_csv(save_var_names, paste0(file_path, "Output/health_extra_var_names.csv"))
```

>>>>

---
title: "Elders health and elder files data cleaning"
author: "Ethan Walker"
date: "Started 28 Feb 2020, Updated 1 March 2021"
output: pdf_document 
---

@@

# Load and merge files from different locations
```{r}
nn_athomelog_initial <- read_xlsx(paste0(file_path, "Input/NN/athomelog.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NN",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         at_home_7 = as.factor(AtHome1),
         at_home_8 = as.factor(AtHome2),
         at_home_9 = as.factor(AtHome3),
         at_home_10 = as.factor(AtHome4),
         at_home_11 = as.factor(AtHome5),
         at_home_12 = as.factor(AtHome6),
         at_home_13 = as.factor(AtHome7),
         at_home_14 = as.factor(AtHome8),
         at_home_15 = as.factor(AtHome9),
         at_home_16 = as.factor(AtHome10),
         at_home_17 = as.factor(AtHome11),
         at_home_18 = as.factor(AtHome12),
         at_home_19 = as.factor(AtHome13),
         at_home_20 = as.factor(AtHome14),
         at_home_21 = as.factor(AtHome15),
         at_home_22 = as.factor(AtHome16)) %>% 
  select(home_winter_id:at_home_22)

npt_athomelog_initial <- read_xlsx(paste0(file_path, "Input/NP/athomelog.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NPT",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         at_home_7 = as.factor(AtHome1),
         at_home_8 = as.factor(AtHome2),
         at_home_9 = as.factor(AtHome3),
         at_home_10 = as.factor(AtHome4),
         at_home_11 = as.factor(AtHome5),
         at_home_12 = as.factor(AtHome6),
         at_home_13 = as.factor(AtHome7),
         at_home_14 = as.factor(AtHome8),
         at_home_15 = as.factor(AtHome9),
         at_home_16 = as.factor(AtHome10),
         at_home_17 = as.factor(AtHome11),
         at_home_18 = as.factor(AtHome12),
         at_home_19 = as.factor(AtHome13),
         at_home_20 = as.factor(AtHome14),
         at_home_21 = as.factor(AtHome15),
         at_home_22 = as.factor(AtHome16)) %>% 
  select(home_winter_id:at_home_22)

# Combine logs from all areas
elders_at_home_log <- rbind(nn_athomelog_initial, npt_athomelog_initial) %>% 
  left_join(elders_ids_linked, c("area", "home_winter_id", "adult_id_num"))
# write_rds(elders_at_home_log, "Output/elders_at_home_log.rds")

@@

# write_csv(save_var_names, paste0(file_path, "Output/at_home_var_names.csv"))
```

@@

# Load and merge files from different locations
```{r}
nn_healthhistory_initial <- read_xlsx(paste0(file_path, "Input/NN/healthhistory.xlsx")) %>% 
  rename_all(~str_replace_all(., "Date", "_date")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NN",
         rheum_arth = ra,
         rheum_arth_date = ra_date) %>% 
  select(-id:-homewinterid, -ra, -ra_date, -whatmissing:-ignorereason) %>% 
  select(home_winter_id, adult_id_num, area, rheum_arth, rheum_arth_date,
         lupus:cigarspipes)

npt_healthhistory_initial <- read_xlsx(paste0(file_path, "Input/NP/healthhistory.xlsx")) %>% 
  rename_all(~str_replace_all(., "Date", "_date")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NPT",
         rheum_arth = ra,
         rheum_arth_date = ra_date) %>% 
  select(-id:-homewinterid, -ra, -ra_date, -whatmissing:-ignoremissingdata) %>% 
  select(home_winter_id, adult_id_num, area, rheum_arth, rheum_arth_date,
         lupus:cigarspipes)

# Combine logs from all areas
elders_health_hx <- rbind(nn_healthhistory_initial, npt_healthhistory_initial) %>% 
  left_join(elders_ids_linked, c("area", "home_winter_id", "adult_id_num"))
# write_rds(elders_health_hx, "Output/elders_health_hx.rds")

@@

#write_csv(save_var_names, paste0(file_path, "Output/health_hx_var_names.csv"))
```

@@

# Load and merge files from different locations
```{r}
nn_healthextra_initial <- read_xlsx(paste0(file_path, "Input/NN/healthextra.xlsx")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NN",
         sampling_visit = samplingvisit) %>% 
  select( home_winter_id, adult_id_num, sampling_visit, area, cold2m:bronch2mdr)

npt_healthextra_initial <- read_xlsx(paste0(file_path, "Input/NP/healthextra.xlsx")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NPT",
         sampling_visit = samplingvisit) %>% 
  select( home_winter_id, adult_id_num, sampling_visit, area, cold2m:bronch2mdr)

# Combine logs from all areas
elders_health_extra <- rbind(nn_healthextra_initial, npt_healthextra_initial) %>% 
  left_join(elders_ids_linked, c("area", "home_winter_id", "adult_id_num"))
# write_rds(elders_health_extra, "Output/elders_health_extra.rds")

@@

# write_csv(save_var_names, paste0(file_path, "Output/health_extra_var_names.csv"))
```

### 2021-03-01 home_adult_data_cleaning.Rmd
data cleaning updates

---
title: "EldersAIR initial home/adult data work"
author: "Ethan Walker"
date: "Started 10 Feb 2020, Updated 10 Aug 2020"
output: pdf_document
---

@@

# Load, format, and save home and adult overview/demographic data 
```{r}
# Load files 
## Box location: Update Box location once final data loaded
np_adult_initial <- read_xlsx(paste0(file_path, "Input/NP/adult.xlsx"), skip = 1,
                               na = c("", "NULL"),
                              col_names = c("adult_id_num", "home_id_num", "adult_id_char",
                                            "hispanic", "age_nov", "race", "gender",
                                            "child_assent", "consent_date", "phi_date",
                                            "phi_dr", "comment", "missing", "incomplete",
                                            "enrolled", "ignore_missing", "ignore_reason"),
                              col_types = c("numeric", "numeric", "text",
                                            "text", "text", "text", "text", 
                                            "text", "date", "date",
                                            "text", "text", "text", "text", 
                                            "text", "text", "text")) %>% 
  mutate(adult_id_num = as.factor(adult_id_num),
         home_id_num = as.factor(home_id_num),
         adult_id_char = as.factor(adult_id_char),
         adult_id_char = gsub("_", "", adult_id_char),
         adult_id_char = gsub(" ", "", adult_id_char),
         consent_date = ymd(consent_date),
         area = "NPT") %>% 
  select(adult_id_num, home_id_num, area, adult_id_char, consent_date, phi_date) %>% 
  arrange(adult_id_num)

@@

elders_adult <- rbind(np_adult_initial, nn_adult_initial)
summary(elders_adult)

# Load files 
## Box location: Update Box location once final data loaded
np_demographics_initial <- read_xlsx(paste0(file_path, "Input/NP/demographics.xlsx"),
                                      na = c("", "NULL")) %>% 
  rename_all(tolower) %>% 
  mutate(adult_id_num = as.factor(adultid),
         home_winter_id = as.factor(homewinterid),
         gender = factor(gender),
         hispanic = factor(hispanic),
         race = factor(race),
         income = factor(income),
         education = factor(education),
         total_residents = as.numeric(totalres),
         residents_under18 = as.numeric(undereighteen),
         age = as.numeric(agenov1),
         area = "NPT") %>% 
  select(adult_id_num, home_winter_id, area, gender, hispanic, race, income, 
         education, total_residents, residents_under18, age) %>% 
  arrange(adult_id_num)

@@

elders_demographics <- rbind(np_demographics_initial, nn_demographics_initial)
summary(elders_demographics)

## Box location: Update Box location once final data loaded
np_homewinter_initial <- read_xlsx(paste0(file_path, "Input/NP/homewinter.xlsx"), 
                                   skip = 1, na = c("", "NULL"),
                              col_names = c("home_winter_id", "home_id_num", "winter_id",
                                            "intervention_date", "intervention_time", 
                                            "sampling_date", "sampling_time", 
                                            "pickup_date", "pickup_time", 
                                            "sampling_date2", "sampling_time2", 
                                            "pickup_date2", "pickup_time2"),
                              col_types = c("numeric", "numeric", "numeric",
                                            "date", "date", 
                                            "date", "date", 
                                            "date", "date", 
                                            "date", "date", 
                                            "date", "date")) %>% 
  separate(intervention_time, c("trash1", "intervention_time"), sep = " ", remove = FALSE) %>%
  separate(sampling_time, c("trash1", "sampling_time"), sep = " ", remove = FALSE) %>%
  separate(pickup_time, c("trash1", "pickup_time"), sep = " ", remove = FALSE) %>%
  separate(sampling_time2, c("trash1", "sampling_time2"), sep = " ", remove = FALSE) %>%
  separate(pickup_time2, c("trash1", "pickup_time2"), sep = " ", remove = FALSE) %>%
  mutate(home_id_num = as.factor(home_id_num),
         winter_id = as.factor(winter_id),
         home_winter_id = as.factor(home_winter_id),
         intervention_date = ymd(intervention_date),
         intervention_time = as.character(intervention_time),
         sampling_date = ymd(sampling_date),
         sampling_time = as.character(sampling_time),
         pickup_date = ymd(pickup_date),
         pickup_time = as.character(pickup_time),
         sampling_date2 = ymd(sampling_date2),
         sampling_time2 = as.character(sampling_time2),
         pickup_date2 = ymd(pickup_date2),
         pickup_time2 = as.character(pickup_time2),
         area = "NPT") %>% 
  select(home_id_num, winter_id, home_winter_id, area, intervention_date, intervention_time,
         sampling_date, sampling_time, pickup_date, pickup_time,
         sampling_date2, sampling_time2, pickup_date2, pickup_time2) %>% 
  filter(winter_id != 3) %>% 
  arrange(home_id_num, winter_id)

@@

elders_homewinter <- rbind(np_homewinter_initial, nn_homewinter_initial)
summary(elders_homewinter)

## Box location: Update Box location once final data loaded
np_home_initial <- read_xlsx(paste0(file_path, "Input/NP/home.xlsx"), na = c("", "NULL")) %>% 
  rename_all(tolower) %>% 
  mutate(home_id_num = as.factor(homeid),
         home = as.factor(home),
         treatment = as.factor(txcondition),
         home = gsub("_", "", home),
         home = gsub(" ", "", home),
         area = "NPT") %>% 
  select(home_id_num, home, treatment, area)

@@

elders_home <- rbind(np_home_initial, nn_home_initial)
```

# Combine adult, home, homewinter files
```{r}
elders_demographics_final <- elders_homewinter %>%
  left_join(elders_demographics, by = c("area", "home_winter_id")) %>% 
  left_join(elders_home, by = c("area", "home_id_num")) %>% 
  left_join(elders_adult, by = c("area", "home_id_num", "adult_id_num")) %>% 
  mutate(intervention_date = gsub("2014-03-14", "2017-03-14", intervention_date)) %>% 
  select(adult_id_num, adult_id_char, area, home, home_id_num, home_winter_id, 
         winter_id, treatment, intervention_date:phi_date) %>% 
  filter(!is.na(home)) %>% 
  mutate(income = factor(income,
                         levels = c("Less than $20,000", "$20,000 to $29,999",
                                    "$30,000 to $39,999", "$40,000 to $49,999",
                                    "$50,000 to $74,999", "$75,000 to $99,999",
                                    "$100,000 or more"),
                         labels = c("< $20,000", "$20,000 to $29,999",
                                    "$30,000 to $39,999", "$40,000 to $49,999",
                                    "$50,000 to $74,999", "$75,000 to $99,999",
                                    ">= $100,000")),
         education = factor(education,
                            levels = c("Less than high school", "High school diploma or GED",
                                       "Some college", "College degree"),
                            labels = c("< high school", "High school grad or GED",
                                       "Some college", "College degree"))) %>% 
  arrange(area, home, winter_id)

>>>>

---
title: "EldersAIR initial home/adult data work"
author: "Ethan Walker"
date: "Started 10 Feb 2020, Updated 1 March 2021"
output: pdf_document
---

@@

# Load, format, and save home and adult overview/demographic data 
```{r}
# Load files 
## Box location: Update Box location once final data loaded
npt_adult_initial <- read_xlsx(paste0(file_path, "Input/NP/adult.xlsx"), skip = 1,
                               na = c("", "NULL"),
                              col_names = c("adult_id_num", "home_id_num", "adult_id_char",
                                            "hispanic", "age_nov", "race", "gender",
                                            "child_assent", "consent_date", "phi_date",
                                            "phi_dr", "comment", "missing", "incomplete",
                                            "enrolled", "ignore_missing", "ignore_reason"),
                              col_types = c("numeric", "numeric", "text",
                                            "text", "text", "text", "text", 
                                            "text", "date", "date",
                                            "text", "text", "text", "text", 
                                            "text", "text", "text")) %>% 
  mutate(adult_id_num = as.factor(adult_id_num),
         home_id_num = as.factor(home_id_num),
         adult_id_char = as.factor(adult_id_char),
         adult_id_char = gsub("_", "", adult_id_char),
         adult_id_char = gsub(" ", "", adult_id_char),
         consent_date = ymd(consent_date),
         area = "NPT") %>% 
  select(adult_id_num, home_id_num, area, adult_id_char, consent_date, phi_date) %>% 
  arrange(adult_id_num)

@@

elders_adult <- rbind(npt_adult_initial, nn_adult_initial)
summary(elders_adult)

# Load files 
## Box location: Update Box location once final data loaded
npt_demographics_initial <- read_xlsx(paste0(file_path, "Input/NP/demographics.xlsx"),
                                      na = c("", "NULL")) %>% 
  rename_all(tolower) %>% 
  mutate(adult_id_num = as.factor(adultid),
         home_winter_id = as.factor(homewinterid),
         gender = factor(gender),
         hispanic = factor(hispanic),
         race = factor(race),
         income = factor(income),
         education = factor(education),
         total_residents = as.numeric(totalres),
         residents_under18 = as.numeric(undereighteen),
         age = as.numeric(agenov1),
         area = "NPT") %>% 
  select(adult_id_num, home_winter_id, area, gender, hispanic, race, income, 
         education, total_residents, residents_under18, age) %>% 
  arrange(adult_id_num)

@@

elders_demographics <- rbind(npt_demographics_initial, nn_demographics_initial)
summary(elders_demographics)

## Box location: Update Box location once final data loaded
npt_homewinter_initial <- read_xlsx(paste0(file_path, "Input/NP/homewinter.xlsx"), 
                                   skip = 1, na = c("", "NULL"),
                              col_names = c("home_winter_id", "home_id_num", "winter_id",
                                            "intervention_date", "intervention_time", 
                                            "sampling_date", "sampling_time", 
                                            "pickup_date", "pickup_time", 
                                            "sampling_date2", "sampling_time2", 
                                            "pickup_date2", "pickup_time2"),
                              col_types = c("numeric", "numeric", "numeric",
                                            "date", "date", 
                                            "date", "date", 
                                            "date", "date", 
                                            "date", "date", 
                                            "date", "date")) %>% 
  separate(intervention_time, c("trash1", "intervention_time"), sep = " ", remove = FALSE) %>%
  separate(sampling_time, c("trash1", "sampling_time"), sep = " ", remove = FALSE) %>%
  separate(pickup_time, c("trash1", "pickup_time"), sep = " ", remove = FALSE) %>%
  separate(sampling_time2, c("trash1", "sampling_time2"), sep = " ", remove = FALSE) %>%
  separate(pickup_time2, c("trash1", "pickup_time2"), sep = " ", remove = FALSE) %>%
  mutate(home_id_num = as.factor(home_id_num),
         winter_id = as.factor(winter_id),
         home_winter_id = as.factor(home_winter_id),
         intervention_date = ymd(intervention_date),
         intervention_time = as.character(intervention_time),
         sampling_date = ymd(sampling_date),
         sampling_time = as.character(sampling_time),
         pickup_date = ymd(pickup_date),
         pickup_time = as.character(pickup_time),
         sampling_date2 = ymd(sampling_date2),
         sampling_time2 = as.character(sampling_time2),
         pickup_date2 = ymd(pickup_date2),
         pickup_time2 = as.character(pickup_time2),
         area = "NPT") %>% 
  select(home_id_num, winter_id, home_winter_id, area, intervention_date, intervention_time,
         sampling_date, sampling_time, pickup_date, pickup_time,
         sampling_date2, sampling_time2, pickup_date2, pickup_time2) %>% 
  filter(winter_id != 3) %>% 
  arrange(home_id_num, winter_id)

@@

elders_homewinter <- rbind(npt_homewinter_initial, nn_homewinter_initial)
summary(elders_homewinter)

## Box location: Update Box location once final data loaded
npt_home_initial <- read_xlsx(paste0(file_path, "Input/NP/home.xlsx"), na = c("", "NULL")) %>% 
  rename_all(tolower) %>% 
  mutate(home_id_num = as.factor(homeid),
         home = as.factor(home),
         treatment = as.factor(txcondition),
         home = gsub("_", "", home),
         home = gsub(" ", "", home),
         area = "NPT") %>% 
  select(home_id_num, home, treatment, area)

@@

elders_home <- rbind(npt_home_initial, nn_home_initial)
```

# Combine adult, home, homewinter files
```{r}
elders_demographics_final <- elders_homewinter %>%
  left_join(elders_demographics, by = c("area", "home_winter_id")) %>% 
  left_join(elders_home, by = c("area", "home_id_num")) %>% 
  left_join(elders_adult, by = c("area", "home_id_num", "adult_id_num")) %>% 
  mutate(intervention_date = gsub("2014-03-14", "2017-03-14", intervention_date)) %>% 
  select(adult_id_num, adult_id_char, area, home, home_id_num, home_winter_id, 
         winter_id, treatment, intervention_date:phi_date) %>% 
  filter(!is.na(home)) %>% 
  filter(!is.na(treatment)) %>% 
  mutate(income = factor(income,
                         levels = c("Less than $20,000", "$20,000 to $29,999",
                                    "$30,000 to $39,999", "$40,000 to $49,999",
                                    "$50,000 to $74,999", "$75,000 to $99,999",
                                    "$100,000 or more"),
                         labels = c("< $20,000", "$20,000 to $29,999",
                                    "$30,000 to $39,999", "$40,000 to $49,999",
                                    "$50,000 to $74,999", "$75,000 to $99,999",
                                    ">= $100,000")),
         education = factor(education,
                            levels = c("Less than high school", "High school diploma or GED",
                                       "Some college", "College degree"),
                            labels = c("< high school", "High school grad or GED",
                                       "Some college", "College degree"))) %>% 
  arrange(area, adult_id_num, winter_id) %>% 
  select(area, home, home_id_num, home_winter_id, winter_id, treatment, 
         adult_id_char, adult_id_num, 
         gender:age, intervention_date:phi_date)
